### 2014-07-23 fundamentals/examples.tex
topic sentences

\section{Verification}
% Organize this section according to major topics
% give each topic a section heading in boldface.
% try to cover the major common points :
%
% problem design
% methods of measurement
% supporting models
% supporting data
% simulations run
% results

@@

Unfortunately, we can't wind forward the clock to compare our simulations to 
the futures that we are attempting to model.

However, Cyclus does implement a number of strategies for verification and 
validation of code.

\subsection{Coding Practices}
% What have we done to ensure robustness ?
% Examples from Material class, Transactions, simulation IDs

Some routines are implemented specifically to ensure robustness.

\subsection{Testing Framework}
% Peer-review system (secretly a note on open source?)

We have reasonable test coverage and a code review system.

\subsection{Benchmarks}
%Inpro benchmark?
%FCO code-to-code?

A simple transition scenario recently used for a code-to-code comparison within 
the national laboratories can demonstrate the ability for Cyclus to conform to 
externally defined specifications.

>>>>

\section{Examples}
% Organize this section according to major topics
% give each topic a section heading in boldface.
% try to cover the major common points :
%
% problem design
% methods of measurement
% supporting models
% supporting data
% simulations run
% results

@@

Current and past simulations with the Cyclus simulator have already 
demonstrated a range of uses.

\subsection{Ecosystem}
% Cycamore library
% Cyder?

External modules have been (cite cyder, separations, streamblender, demandinst, 
commodconverter, etc.) and are being (cite brightlight, UTK module, etc.) 
developed for contribution to the cyclus ecosystem of models.

\subsection{Simulations}
%FCO example (will be done soon.. publishable?)
%Inpro example (is this still running or did we deprecate it with 1.0?)

Simulations have been run in the past and more are being run. FCO is an 
example.
